Citation Analysis of Computer Science

### 2019-11-17 Scientometrics/comp.tex
udpate

Computer science, and its applications, has experienced rapid growth and diversification over the last twenty years. As noted in a 2017 US National Academies Report~\cite{nas_2017}, ``A wide range of jobs in virtually all sectors demand computing skills to an unprecedented extent. And every academic discipline finds itself incorporating computing into its research and educational mission". The collective influence of the Internet of Things (IoT), `big' data, accessible cloud computing, and advances in artificial intelligence have been postulated as a recent driver for growth and evolution~\cite{siebel2019_digital} of computing.

@@

Obviousy, much in the way of growth and evolution of computing has occurred since 1974. Progressing beyond the historical triad of theoretical foundations; hardware and computer systems; and software, the Computing Classification System (CCS)~\cite{acm_ref} published by the Association for Computing Machinery now consists of 13 top-level areas that reflect a more current view of the field. This classification does address relationships with other fields under Applied Computing. However, an easy way to map scientific publications, especially interdisciplinary articles or those from adjacent fields, to the CCS classification does not exist.

 \emph{I'd like to see some text about (i) limited funding resources (ii) efficient use of existing resources (iiii) informing policy at multiple levels -- all directed at justifying our study. I'm not sure where to put it though. George look at Daniel Sarewitz' papers. This could be moved to the Discussion.Porter and colleagues in a study on measuring interdisciplinarity~\cite{porter_measuring_2007} observe that 'The discrepancies between disciplinary roots and research realities loom large', a reference to the challenges associated with knowledge diffusing across researchers who tend to be focused in their own areas. This concern may be especially relevant for computer science given the ubiquity of computing today and limited public funding for research. }

@@

%%%%%%%%%%%%%%%
\section{Materials and Methods}

@@

>>>>

Computer science, and its applications, has experienced rapid growth and diversification over the last twenty years. The collective influence of the Internet of Things (IoT), `big' data, accessible cloud computing, and advances in artificial intelligence have further been postulated as a recent driver for its growth and evolution~\cite{siebel2019_digital}. As also noted in a 2017 US National Academies Report~\cite{nas_2017}, ``A wide range of jobs in virtually all sectors demand computing skills to an unprecedented extent. And every academic discipline finds itself incorporating computing into its research and educational mission".

Given this powerful influence of computer science in research, some understanding its present state, structure, and relationship to other fields that goes beyond satisfying mere interest seems warranted since it would inform planning and policy making at multiple levels from national level funding all the way down to faculty hiring strategy. In using the term inform, we are mindful of (i) Greenhalgh (ii) Sarewitz and Pielke. \emph{I think that I want to cite these two without really knowing how. Greenhalgh for the limitations of positivism. Sarewitz for the limitations of allowing science to do whatever it wants to. I'd also like to see some text about (i) limited funding resources (ii) efficient use of existing resources (iiii) informing policy at multiple levels -- all directed at justifying our study. I'm not sure where to put it though. CS can also be an excellent model system for studying interdisciplinarity cite Porter and colleagues in a study on measuring interdisciplinarity~\cite{porter_measuring_2007 } observe that 'The discrepancies between disciplinary roots and research realities loom large', a reference to the challenges associated with knowledge diffusing across researchers who tend to be focused in their own areas. This concern may be especially relevant for computer science given the ubiquity of computing today and limited public funding for research. Maybe squeeze in Tandy's NAS report on interdisciplinarity. I should ping Ohid Yaqub about this too- science policy is his area.}

@@

Much in the way of growth and evolution of computing has occurred since 1974. Progressing beyond the historical triad of theoretical foundations; hardware and computer systems; and software, the Computing Classification System (CCS)~\cite{acm_ref} published by the Association for Computing Machinery now consists of 13 top-level areas that reflect a more current view of the field. This classification does address relationships with other fields under Applied Computing. However, an easy way to map scientific publications, especially interdisciplinary articles or those from adjacent fields, to the CCS classification does not exist.

@@

\section{Materials and Methods}

@@

\emph{need to cite Granovetter somewhere for definition of strong and weak ties that Small refers to}
